title: Phat Si Ew 


inspiration: Adapted from Andy Ricker, Pok Pok 


requires: really big pan / wok

tags: thai, noodle, main, 

elapsed time: 20 min

servings: lots 


ingredients: 

	16 oz fresh wide flat rice noodles \footnote{chow fun or phat see ew noodles, find them in the produce/fresh section of asian grocery}
	3 eggs
	4 tbsp minced garlic
	8 oz gai lan
	1 lb chicken, pork loin, tofu or mixed. 

	sauce: 
		3 tbsp light soy sauce
		3 tsp dark soy sauce
		2 tsp sugar
		4 tsp fish sauce


If meat: 
	Chop meat into 1/8 -inch thick strips or pieces.
	Heat 1 tbsp peanut oil in wok over high heat.
	Fry meat pieces until cooked. 
	(Book suggestion: mix with 1 tsp of the fish sauce and an extra ½ tsp of sugar as you are cooking the meat.)
	Remove from wok.
If Tofu: 
	Cut block into 1/8 inch strips 

Mix the soy sauces, sugar, and the rest of the fish sauce together in a bowl (sauce ingredients)

Set water to boil.
Carefully separate all the noodles from each other (takes longer than expected 6 min)
Plunge them in boiling water for ~10 seconds.
Remove them and drain well. 

Heat 2 tbsp peanut oil in wok over high heat.
Crack eggs into wok, cook without touching until the edges turn light golden brown.
Flip the eggs and push to one side of the wok.

(good place to pause recipe)
Keep the wok at high heat.
Add noodles and garlic, stirring lightly.
Break up the egg and mix together, until warm.
Add the gai lan and stir-fry until wilted. 
Add the meat/tofu and soy sauce mixture (use splash of water to get all the sugar from the bowl).
Stir-fry until the meat is heated and the noodles absorb the liquids, about 1 minute.
Remove from heat and season to taste with fish sauce (and sugar). 
